Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-03 manuscript-chicago.Rmd
Add introduction header and small edits

bibliography      : ["references.bib"]

@@

Prior to the advent of social media, people coordinated their protest behavior
using phone tree calling sheets and mimeographed flyers, through in-person
meetings of social organizations and churches, and through word of mouth. They
gathered together and hand-made protest signs that reflected their agendas. As
McAdam found, people were more likely to join movements when they had a personal
connection [@mcadam1986recruitment; @mcadam1993specifying]: Historically, strong
ties have been strong predictors of involvement in high-risk protest activity.

>>>>

bibliography      : ["references.bib"]
csl               : chicago.csl

@@

## Introduction
Prior to the advent of social media, people coordinated their protest behavior
using phone tree calling sheets and mimeographed flyers, through in-person
meetings of social organizations and churches, and through word of mouth. They
gathered together and hand-made protest signs that reflected their agendas. As
McAdam found, people were more likely to join movements when they had a personal
connection [@mcadam1986recruitment; @mcadam1993specifying]: Historically, strong
ties have been strong predictors of involvement in high-risk protest activity.
